```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

options(knitr.table.format = "latex",
        knitr.kable.NA = '')

```

\hfill \break

\hfill \break

\hfill Fiscal 2023 TLS Budget for `r x` \hfill \hfill \hfill \break

`r agency` Agency Head / Fiscal Officer \hfill March 1, 2022

\hfill \break

On behalf of Budget Director, Robert Cenname, below are the General Fund Target Level of Service (TLS) Budget figures for Fiscal 2023. Please note that Fiscal 2023 preliminary budget decisions are not yet final; these figures are subject to change as the budget planning cycle proceeds. If your agency’s General Fund target level of service changes, BBMR will notify and work with you to make any necessary adjustments in our budgeting system.

Your BBMR analyst is available for any questions or support. Please work with your analyst regarding any additional changes needed to your current line item budgets in BPFS, including all Funds.

```{r}
numbers %>%
  #select(`FY23 CLS`, `FY23 TLS`, Change = `FY23 CLS to FY23 TLS Change`) %>%
  mutate_if(is.numeric, scales::dollar, negative_parens = TRUE) %>%
  kable(booktabs = TRUE, align = c("l", rep("r", 3))) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1:3, width = "1in") 
```


```{r}

updates %>%
  bookHelpers::bind_total_row(total_col = "Update", total_name = "TOTAL") %>%
  mutate_if(is.numeric, scales::dollar, negative_parens = TRUE) %>%
  kable(booktabs = TRUE, align = c("r", "l", "l")) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(nrow(l$update), hline_after = TRUE) %>%
  row_spec(nrow(l$update) + 1, bold = TRUE) %>%
  column_spec(1, width = "1in") %>%
  column_spec(2, width = "2.5in") %>%
  column_spec(3, width = "2.5in")


```
