```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

options(knitr.table.format = "latex",
        knitr.kable.NA = '')

agency_clean <-info$agencies$`Agency Name - Cleaned`[info$agencies$`Agency ID` == x]

```

\hfill \break

\hfill \break

\hfill Fiscal 2024: Target Level of Service \hfill \hfill \hfill \break

`r agency_clean` Agency Head/Fiscal Officer \hfill \hfill `r format(Sys.Date(), format="%B %d %Y")`

```{r Total Budget, echo = FALSE, warning = FALSE}

df <- tls %>%
  filter(`Agency Name` == agency & `Fund ID` == 1001) %>%
  ungroup() %>%
  select(-`Fund Name`, -`Agency ID`, -`Agency Name`, -`% - Change vs Adopted`, -`$ - Change vs Adopted`)

total <- scales::dollar(sum(df$`FY24 TLS`, na.rm = TRUE), style_negative = "parens")

```


**Fiscal Year 2024 TLS Amount: `r total `**

Your agency’s Fiscal Year 2024 Target Level of Service (TLS) amount is included below. The table below summarizes your agency’s budget by fund-service. Your Budget Analyst is available to answer specific questions regarding changes reflected in the TLS budget amounts.

```{r TLS Table, echo = FALSE, warning = FALSE}

output <- df %>%
  group_by(Service) %>%
  summarise_if(is.numeric, sum, na.rm = TRUE) %>%
  select(-`Fund ID`) %>%
  adorn_totals(where = "row", name = "Agency General Fund Total")

output %>%
  format_table_numbers() %>%
  format_table(longtable = TRUE, align = c("l", rep("r", 4))) %>%
  column_spec(1, width = "2.5in") %>%
  column_spec(2:5, width = "1.0in") %>%
  kable_styling(latex_options = c("striped"), 
                fixed_thead = FALSE, font_size = 10) %>%
  row_spec(0, bold = TRUE)

```

Please contact your Budget Analyst if you have additional questions regarding the FY 2024 planning process.

<!-- \backgroundsetup{contents={}} -->