```{r setup, include=FALSE}
options(tinytex.verbose = FALSE)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

options(knitr.table.format = "latex",
        knitr.kable.NA = '',
        knitr.table.vline = "")

```

\hfill \break

\hfill \break

\hfill Fiscal 2024: Target Level of Service \hfill \hfill \hfill \break

`r agency_clean` Agency Head/Fiscal Officer \hfill \hfill `r format(Sys.Date(), format="%B %d %Y")`

```{r Total Budget, echo = FALSE, warning = FALSE}

df <- data %>%
  filter(`Agency Name` == agency & `Fund ID` == 1001) %>%
  ungroup() %>%
  select(-`Fund Name`, -`Agency ID`, -`Agency Name`, -`% - Change vs Adopted`, -`$ - Change vs Adopted`)

total <- scales::dollar(sum(df$`FY24 TLS`, na.rm = TRUE), style_negative = "parens")

```


**Fiscal Year 2024 TLS GF Amount: `r total `**

Your agency’s Fiscal Year 2024 Target Level of Service (TLS) General Fund amount is included below. The table summarizes your agency’s budget by service. Your Budget Analyst is available to answer specific questions regarding changes reflected in the TLS budget amounts.

```{r TLS Table, echo = FALSE, warning = FALSE}

output <- df %>%
  group_by(Service) %>%
  summarise_if(is.numeric, sum, na.rm = TRUE) %>%
  select(-`Fund ID`) %>%
  adorn_totals(where = "row", name = "Agency General Fund Total")

output %>%
  format_table_numbers() %>%
  kable(longtable = TRUE, booktabs = TRUE,
      format = "latex", escape = TRUE,
      align = c("l", rep("r", 4))) %>%
  column_spec(1, width = "2.6in") %>%
  column_spec(2:5, width = ".9in") %>%
  kable_styling(latex_options = "striped", font_size = 10) %>%
  row_spec(nrow(output), bold = TRUE) %>%
  row_spec(0, bold = TRUE, align = "c", background = "#19315f", color = "white")

```

Please contact your Budget Analyst if you have additional questions regarding the FY 2024 planning process.

<!-- \backgroundsetup{contents={}} -->